% Last updated: 1/18/2025
\documentclass{joel_cv}

\begin{document}

% Name, phone, email, address
\begin{cvHeader} 
    \printName{Ting-Hsuan Chao (Joel)}
    \printEmail{joelthchao@gmail.com}
\end{cvHeader}

%
% Experience
%

\sectionTitle{Experience}

\begin{profExp}
    {Dcard - Engineering Manager, ML}{2022/10 - present}{
        \begin{itemize}
            \item Led a cross-functional team of 10+ ML, backend, and data engineers, delivering multiple high-impact projects with measurable business outcomes.
            \item Achieved a 30\%+ increase in user duration by optimizing the post recommendation system with advanced modeling techniques and system enhancements.
            \item Achieved a 35\%+ increase in ad CTR by shaping business models, identifying key opportunities for model improvement, and resolving performance bottlenecks.
            \item Doubled search volume and improved search success rate by transforming the search recommendation system from rule-based to learning-based methodologies.
            \item Designed a next-generation data architecture and developed easy-to-use data models, enhancing scalability, accessibility, and enabling data-driven decision-making.
            \item Built robust MLOps systems that streamlined ML workflows, accelerated iteration speed, and improved infrastructure stability to support growth.
        \end{itemize}
    }
\end{profExp}

\begin{profExp}{Dcard - Senior Machine Learning Engineer}{2020/10 - 2022/10}{
        \begin{itemize}
            \item Led the development of the post recommendation system, significantly improving user experience.
            \item Defined and executed product and technical roadmaps to align with business objectives.
            \item Conducted data analytics and developed algorithms to enhance recommendation precision.
            \item Designed and implemented robust data pipelines to ensure reliability and efficiency in data processing.
            \item Optimized experiment design and A/B testing procedures, improving the accuracy and speed of decision-making processes.
        \end{itemize}
    }
\end{profExp}

\begin{profExp}{Baidu Inc. - Senior NLP Engineer}{2018/09 - 2020/02}{
        \begin{itemize}
            \item Social network app recommendation system design
            \item Stamp suggestion by text intention understanding
            \item Japanese website recommendation system by Elasticsearch and CTR prediction
            \item Input method editor Emoji prediction by language modeling
            \item Increase neural conversation diversity by maximizing mutual information
            \item Research Japanese word embedding methods and leverage in subtasks to improve performance
        \end{itemize}
    }
\end{profExp}

\begin{profExp}{Appier Inc. - Machine Learning Scientist}{2016/05 - 2018/08}{
        \begin{itemize}
            \item Large-scale multi-languages user topic module from Spark, AI algorithm, database to APIs
            \item Research on Chinese natural language understanding
            \item Scalable and robust machine learning ensemble framework
            \item Real-time user purchase intent prediction by RNN
            \item Automatic advertisement bidding bot by Reinforcement Learning
            \item Data augmentation by Generative Adversarial Networks for cross device user identification
        \end{itemize}
    }
\end{profExp}

\begin{profExp}{National Taiwan University - Research Assistant}{2015/08 - 2016/05}
    {
        \begin{itemize}
            \item Advanced research on deep learning compression and speedup
        \end{itemize}
    }
\end{profExp}

\begin{profExp}{Hewlett-Packard, Inc - Software Engineer Intern}{2012/07 - 2013/06}{
        \begin{itemize}
            \item Develop and maintain softpaq checking tool, wireless diagnose tool, and web service APIs
        \end{itemize}
    }
\end{profExp}

%
% Education
%

\sectionTitle{Education}
\begin{sectionContentSimple}{National Taiwan University}{2013/09 - 2015/07}
    \item M.S. in Computer Science \& Information Engineering
    \item Communications and Multimedia Laboratory (CMLAB), MiRA Group
    \item Advisor: Winston H. Hsu
\end{sectionContentSimple}

\begin{sectionContentSimple}{National Taiwan University}{2009/09 - 2013/07}
    \item B.S. in Electrical Engineering
\end{sectionContentSimple}

%
% Publications
%

\sectionTitle{Publications}
\begin{sectionItemize}{$\cdot$}
    \item \underline{Ting-Hsuan Chao}, Yen-Liang Lin, Yin-Hsi Kuo and Winston H. Hsu, "Scalable Object Detection by Filter Compression with Regularized Sparse Coding," CVPR 2015. \href{http://www.cv-foundation.org/openaccess/content_cvpr_2015/html/Chao_Scalable_Object_Detection_2015_CVPR_paper.html}{(Full paper)}
    \item Wei-Tsung Lin, \underline{Ting-Hsuan Chao}, Jian-Min Wu, Tian-Huang Su, "Predict Emoji Combination with Retrieval Strategy", ACM Multimedia 2015. \href{https://www.anlp.jp/proceedings/annual_meeting/2019/pdf_dir/B2-5.pdf}{(Short paper)}
    \item Yu-Hsiu Chen, \underline{Ting-Hsuan Chao}, Yen-Liang Lin and Winston H. Hsu, "Filter-Invariant Image Classification on Social Media Photos", ACM Multimedia 2015. \href{http://dl.acm.org/citation.cfm?id=2806348}{(Short paper)}
    \item Wei-Tse Sun, \underline{Ting-Hsuan Chao}, Yin-Hsi Kuo and Winston H. Hsu "Photo Filter Recommendation by Category-Aware Aesthetic Learning", IEEE Transactions on Multimedia 2017. \href{http://joelthchao.github.io/pdf/photo_sun_tmm_2017.pdf}{(Journal paper)}
    \item Wen-Yu Lee, Yin-Hsi Kuo, Peng-Ju Hsieh, Wen-Feng Cheng, \underline{Ting-Hsuan Chao}, Hui-Lan Hsieh, Chieh-En Tsai, Hsiao-Ching Chang, Jia-Shin Lan, Winston Hsu, "Unsupervised Latent Sub-events Discovery based on Multi-content and Human Activities Analysis for Diverse Event Summarization", ACM Multimedia 2015. \href{http://dl.acm.org/citation.cfm?id=2809935}{(Grand Challenge)}
    \item Chun-yen Yeh, Yu-Chuan Su, Hsin-Fu Huang, \underline{Ting-Hsuan Chao}, Sebastian Agethen, Winston H. Hsu, "Low-Bitrate and Online Mobile Video Classification", ICCE 2016. (Short paper)
\end{sectionItemize}

%
% ACADEMIC EXPERIENCE
%

\sectionTitle{Academic Experience}
\begin{sectionItemize}{$\cdot$}
    \item Reviewer for IEEE Transactions on Multimedia (TMM)
    \item Poster Presentation in CVPR 2015, Boston, USA
    \item Poster Presentation in ACM Multimedia 2015, Brisbane, Australia
\end{sectionItemize}

%
% Projects
%

\sectionTitle{Projects}

\begin{proj}{Keras - Contributor}
    {Deep Learning $\diamond$ Tensorflow $\diamond$ Theano $\diamond$ Python}
    \item A high-level neural networks API, written in Python. Commit over 600+ lines, including a image preprocessing module, a locally connected layer and bug fixes. Answer 140+ issues and resolve 120+ of them.
\end{proj}

\begin{proj}{Kaggle - National Data Science Bowl}
    {Deep Learning $\diamond$ Caffe $\diamond$ CNN $\diamond$ Computer Vision}
    \item Learn to recognize plankton by training convolutional neural networks. Rank $51^{th} (4.9\%)$ in competition.
\end{proj}

\begin{proj}{Kaggle - Carvana Image Masking Challenge}
    {Deep Learning $\diamond$ Keras $\diamond$ Image segmentation $\diamond$ Computer Vision}
    \item Learn to segment car from background by training fully convolutional neural netword. Blonze plate.
\end{proj}

%
% Technical Strengths
%

\sectionTitle{Technical Strengths}
\begin{sectionItemize}{$\cdot$}
    \item Programming Language: Python, Scala, C++, JAVA, MATLAB, javascript
    \item Framework: Keras, TensorFlow, PyTorch, Spark, Caffe, Android, node.js
\end{sectionItemize}

\end{document}
